Results

### 2019-02-27 02_analysis.Rmd
Save prior images

```{r priors-likely, fig.width=2.75, fig.height=1.5, fig.align="center"}
likely_theta <- ggplot(data = tibble(x = c(0, 1)), aes(x = x)) +
  geom_area(stat = "function", fun = dbeta, args = list(shape1 = 5, shape2 = 5), 
            fill = "grey80", color = "black") +
  labs(x = expression(Probability ~ of ~ being ~ likely ~ to ~ donate ~ (theta)), y = "Density") +
  annotate(geom = "label", x = 0.5, y = 1, label = "Beta(5, 5)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)
likely_theta
```

@@

amount_nu + amount_mu + amount_sigma
```

>>>>

```{r priors-likely, fig.width=2.75, fig.height=1.5, fig.align="center"}
likely_theta <- ggplot(data = tibble(x = c(0, 1)), aes(x = x)) +
  geom_area(stat = "function", fun = dbeta, args = list(shape1 = 5, shape2 = 5), 
            fill = "grey80", color = "black") +
  labs(x = expression(Probability ~ of ~ being ~ likely ~ to ~ donate ~ (theta)), y = "Density") +
  annotate(geom = "label", x = 0.5, y = 1, label = "Beta(5, 5)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)
likely_theta

likely_theta %T>% 
  ggsave(., filename = here("output", "figures", "prior-likely.pdf"),
         width = 2.75, height = 1.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "prior-likely.png"),
         width = 2.75, height = 1.5, units = "in", type = "cairo", dpi = 300)
```

@@

amount_priors <- amount_nu + amount_mu + amount_sigma
amount_priors

amount_priors %T>% 
  ggsave(., filename = here("output", "figures", "prior-amount.pdf"),
         width = 8, height = 1.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "prior-amount.png"),
         width = 8, height = 1.5, units = "in", type = "cairo", dpi = 300)
```
